Exploring Multi-Scale Spatiotemporal Twitter User Mobility Patterns with a Visual-Analytics Approach

### 2016-12-09 ijgi-148112-for proofreading/ijgi-148112-can be published_application.tex
have no idea

%=================================================================
\firstpage{1}
\makeatletter 
\setcounter{page}{\@firstpage}
\makeatother 
\articlenumber{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2016}
\copyrightyear{2016}
\externaleditor{Academic Editors: Marguerite Madden and Wolfgang Kainz}
\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: date}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,2}$, Yizhao Gao $^{1,2}$, Zhenhong Du $^{2,4}$ and Shaowen Wang $^{1,2,3,*}$}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu, ygao29@illinois.edu, shaowen@illinois.edu\\
$^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
$^{3}$ \quad National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
$^{4}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}

% Contact information of the corresponding author
\corres{Correspondence: shaowen@illinois.edu}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper, and are grateful for insightful inputs to the early stage of this research received from Yan Liu and Kiumars Soltani in the CyberInfrastructure and Geospatial Information Laboratory at the University of Illinois at Urbana-Champaign. This material is based in part upon work supported by the U.S. National Science Foundation (NSF) under grant numbers: 1354329 and 1443080. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the views of NSF.
Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Shaowen Wang conceived the ideas; Junjun Yin and Yizhao Gao conducted the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin, Yizhao Gao, Zhenhong Du and Shaowen Wang wrote the paper.}

>>>>

%=================================================================
\firstpage{1}
\makeatletter 
\setcounter{page}{\@firstpage}
\makeatother 
\articlenumber{187}
\doinum{10.3390/ijgi5100187}
\pubvolume{5}
\pubyear{2016}
\copyrightyear{2016}
\externaleditor{Academic Editors: Marguerite Madden and Wolfgang Kainz}
\history{Received: 15 August 2016; Accepted: 28 September 2016; Published: 10 October 2016}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

% Authors, for the paper (add full first names)
\Author{Junjun Yin $^{1,2}$ and Zhenhong Du $^{3,*}$}
% Authors, for metadata in PDF
\AuthorNames{Junjun Yin and Zhenhong Du}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Geography and Geographic Information Science, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA; jyn@illinois.edu\\
$^{2}$ \quad CyberGIS Center for Advanced Digital and Spatial Studies, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA\\
$^{3}$ \quad Institute of Geographic Information Science, School of Earth Sciences, Zhejiang University, Hangzhou 310028, China; duzhenhong@zju.edu.cn}

% Contact information of the corresponding author
\corres{Correspondence:duzhenhong@zju.edu.cn; Tel.: +86-138-1919-2989}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{
The authors would like to thank the four anonymous reviewers of IJGI for their constructive comments that better shaped the paper.
Junjun Yin would like to thank the funding support from the U.S. National Science Foundation under grant numbers: ACI-1047916, BCS-0846655, and IIS-1354329.
Zhenhong Du would like to thank the funding support from the Fundamental Research Funds for the Central Universities under grant number:2016XZZX004-02.
The work also used the ROGER supercomputer, which is supported by NSF under grant number: 1429699.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Junjun Yin conceived and designed the experiments; Junjun Yin and Zhenhong Du analyzed the results; Junjun Yin and Zhenhong Du wrote the paper.}
